Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-06-26 paper/paper.tex
details

All in all, the mere existence of a strong LAE galaxy with a broad,
symmetric line is interesting. 
\tol's line shape is different to others and reveals an unexpected
kinematic structure.
A definitive confirmation of our kinematic findings has
to be provided by new observational tests with integral field unit
spectroscopy. 
If our results are confirmed, this would support the multiphase model
as a tool to study the evolutionary link between star-forming and
quiescent stages of dwarf galaxy evolution.

>>>>

All in all, the mere existence of a strong LAE galaxy with a broad,
highly symmetric line is interesting. 
\tol's line shape is different to others and seems to reveal an
unexpected kinematic structure.
A definitive confirmation of our findings has to be provided by new
observational tests with integral field unit spectroscopy. 
A confirmation of our results would support the multiphase model
as a tool to study the evolutionary link between star-forming and
quiescent stages of dwarf galaxy evolution.
